Viscous Transport in Eroding Porous Media

### 2019-07-31 docs/transport/erosion_transport.tex
editing in transport paper

\begin{figure}[htbp]
\begin{center}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r1h_shear}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r0d5h_shear}
\includegraphics[width = 0.38 \textwidth]{./figs/1b_0d4r0d1h_shear}
\caption{\label{fig:NearWall} 
  A single body eroding in Stokes flow. The color indicates the shear
  stress on the body. Therefore, erosion is fastest in the yellow
  regions and slowest in the blue regions.  In this simulation, we use
  three minimum body-to-wall initial distances $d=h$ (left), $h/2$
  (middle), and $h/10$ (right) with $N_\iin = 256$ discretization points
  on the body, a time step size of $\Dt=10^{-4}$, and smoothing
  parameters $\eps = 15/256$ and $\sigma=10/256$.}
\end{center}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{20 nearly touching bodies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We consider 20 eroding bodies initially placed in $[-1,1] \times
[-1,1]$.  The background flow is the Hagen-Poiseuille flow
\begin{align}
  \UU(\xx)=U \left[
  \begin{array}{c}
    1-y^2 \\ 0
  \end{array}
  \right],
\end{align}
where the flow rate $U$ is chosen so that the pressure drop from $x=-2$
to $x=2$ is held fixed at 2.  For equispaced instances of the
configuration are plotted in Figure~\ref{fig:Eroding20vort}.  The color
in these plots is the vorticity, and this can be used to determine
regions of high and low erosion---erosion happens fastest along regions
of the eroding bodies with a large vorticity in magnitude.  In
Figure~\ref{fig:Eroding20flowrate}(a), we plot the area fraction as a
function of normalized time.  Initially, 62\%  of the geometry eroded
bodies corresponding to a porosity of $0.38$.  As the bodies erode, the
area fraction decreases towards 0.  The trend of the area fraction
resembles that of our previous work~\cite{qua-moo2018} (Figure 10(a)),
but with a larger initial area fraction.  We also compute the flow rate
$U$ required to maintain a constant pressure drop across the channel in
Figure~\ref{fig:Eroding20flowrate}(b).  Again, the trend of $U$
resembles that of our previous work~\cite{qua-moo2018} (Figure 10(b)),
except that the initial flow rate is an order of magnitude smaller
because of the larger initial area fraction.

>>>>

\begin{figure}[htbp]
\begin{center}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r1h_shear}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r0d5h_shear}
\includegraphics[width = 0.38 \textwidth]{./figs/1b_0d4r0d1h_shear}
\caption{\label{fig:NearWall} 
  A single body eroding in Stokes flow. The color indicates the shear
  stress on the body in log scale. Therefore, erosion is fastest in the red
  regions and slowest in the blue regions.  In this simulation, we use
  three minimum body-to-wall initial distances $d=h$ (left), $h/2$
  (middle), and $h/10$ (right) with $N_\iin = 256$ discretization points
  on the body, a time step size of $\Dt=10^{-4}$, and smoothing
  parameters $\eps = 15/256$ and $\sigma=10/256$.}
\end{center}
\end{figure}
\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r1h_vort}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r0d5h_vort}
\includegraphics[width = 0.33 \textwidth]{./figs/1b_0d4r0d1h_vort}
\caption{\label{fig:NearWall_vort} The vorticity of the fluid with a single body eroding 
at time t=0.1001. The initial distances from body to wall are $h$ (left), $h/2$
  (middle), and $h/10$ (right).  }
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{20 nearly touching bodies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We consider 20 eroding bodies initially placed in $[-1,1] \times
[-1,1]$.  The background flow is the Hagen-Poiseuille flow
\begin{align}
  \UU(\xx)=U \left[
  \begin{array}{c}
    1-y^2 \\ 0
  \end{array}
  \right],
\end{align}
where the flow rate $U$ is chosen so that the pressure drop from $x=-2$
to $x=2$ is held fixed at 2.  For equispaced instances of the
configuration are plotted in Figure~\ref{fig:Eroding20vort}.  The color
in these plots is the vorticity, and this can be used to determine
regions of high and low erosion---erosion happens fastest along regions
of the eroding bodies with a large vorticity in magnitude.  In
Figure~\ref{fig:Eroding20flowrate}(a), we plot the area fraction as a
function of normalized time.  Initially, 62\%  of the geometry eroded
bodies corresponding to a porosity of $0.38$.  As the bodies erode, the
area fraction decreases towards 0.  The trend of the area fraction
resembles that of our previous work~\cite{qua-moo2018} (Figure 10(a)),
but with a larger initial area fraction.  We also compute the flow rate
$U$ required to maintain a constant pressure drop across the channel in
Figure~\ref{fig:Eroding20flowrate}(b).  Again, the trend of $U$
resembles that of our previous work~\cite{qua-moo2018} (Figure 10(b)),
except that the initial flow rate is an order of magnitude smaller
because of the larger initial area fraction.
